mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-12 Draft3.Rmd
few additions

>>>>

## Basic elements

`mathml` contains several basic elements used in everyday mathematical expressions. For example it is possible to print the function for the linear regression as:

```{r, results='asis'}

term <- quote(hat(y) == hat(b)["0"] + hat(b)["1"]*x)
mathout(term)

# or with greek letters as:

term <- quote(y == beta["0"] + beta["1"]*x + ... + varepsilon["i"])
mathout(term)
```

```{r, results='asis'}

f <- function(x, a)
{
    if(a == 0) return(+Inf);
    if(a == 0) return(-Inf);
    if(a > 1L ) return(frac(1L,2L))
}
mathout(f)
